---
title: "R Notebook"
output: html_notebook
---

Objective :- Calculating the seasonality index using the method of averages and deseasonalizing the demand


Lets load the required libraries
```{r}
library(forecast)
library(stats)
library(data.table)
library(TTR)
library(tseries)
library(astsa)
library(xts)
```

Lets upload the demand data and convert it into time series
The monthly demand of the product over three years is given

```{r}
ts.demand <- ts(demanddata, frequency = 12, start = c(2013,1))
plot(ts.demand,xlab="Year", ylab = "Product Demand")
```


Lets run the Dickey Fuller test to test the stationarity of the model.

Null Hypothesis        H0: Data is not Stationary
Alternative Hypothesis H1: Data is Stationary
```{r}
adf.test(ts.demand,alternative="stationary")
```

The high p-value indicates that the null hypothesis will be rejected. Hence the alternate hypothesis is true i.e. the series is 
stationery.

Lets find the trend, seasonality and the Irregular component using decompose function.

```{r}
decompose.demand <- decompose(ts.demand, "multiplicative")
plot(decompose.demand)
```

The Seasonality is considered to be multiplicative and the same index is used to deseasonilize the demand data.

```{r}
Seasonal_Index <- decompose.demand$figure
Seasonal_Index
Deseasonalized_demand <- ts.demand / Seasonal_Index
round(Deseasonalized_demand,0)

```

```{r}
plot(round(Deseasonalized_demand,0))
```

We get the plot of deseasonalized demand as well as the table of the deseasonalized data


